### 2021-03-31 Chapter-3/Chapter-3.tex
Updates from Overleaf

\section{Side-channel Leakages}
This section discusses two types of side-channel leakage code patterns. The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as secret-dependent control flow transfers and secret-dependent data accesses. Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
\subsection{Control Flow}
\begin{figure}[h]
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_key]    
and   eax, [addr_message] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

@@

>>>>

\section{Side-channel Leakages}
This section discusses two types of side-channel leakage code patterns. The key intuition is that the target application shows different control flows or data flows when it processes different sensitive input data. We refer them as secret-dependent control flow transfers and secret-dependent data accesses. Unlike previous work, our tool works on the machine code, which can provide us more prevision than the previous tools.
\subsection{Control Flow}
\begin{figure}[h]
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
int example1(uint8_t k, uint32_t m) {
  uint32_t b = (k & m) >> 7;
  if (b) {
    ...    // Branch 1
  } else {
    ...    // Branch 2
  }
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
push  ebp
mov   ebp, esp
movzx eax, [addr_k]    
and   eax, [addr_me] 
shr   eax, 0x7           
test  eax, eax
jne   branch 2
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

@@

The first type of leakage sites is secret-dependent control-flow leakage sites. Shown in Figure~\ref{fig:chapter3:cf}(a), the
